---
author: "John East"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---
```{r include = FALSE}
library(readr)
library(dplyr)
library(ggplot2)

Sys.Date()

# Loading Exoplanet Data
pl_data <- read_csv("planets.csv", n_max = 500)

# Selecting Columns
pl_data_clean_1 <- pl_data %>%
  select(pl_name, hostname, discoverymethod, disc_year, disc_facility, pl_bmassj)

# Discovery Plot
pl_exo <- ggplot(pl_data_clean_1, aes(x =disc_year, pl_bmassj, color = discoverymethod)) +
      geom_point(position = "jitter", alpha = 0.5, size = 2) +
      scale_y_log10() +
      ggtitle("ExoPlanet discovered by mass over years") +
      labs(color = "Discovery Method") +
      xlab("Discovery Year") +
      ylab("Planet Mass")


# Facility plot  
fl_exo <- ggplot(pl_data_clean_1, aes(disc_facility, fill = disc_facility)) + geom_bar()

fl_exo_plot <- fl_exo + coord_flip() + theme_bw() + labs(title = "Number of ExoPlanets Discovered by Facility", x = "Facility", y = "Count") + theme(legend.position = "none")

# K2 filter for number of Discoveries
K2_fac <- pl_data_clean_1 %>%
            filter(disc_facility == "K2") %>%
            count(disc_facility)

# CoRoT Filter for number of discoveries
CoRoT <- pl_data_clean_1 %>%
            filter(disc_facility == "CoRoT") %>%
            count(disc_facility)
```

# EXOPLANET DISCOVERIES

### Summary
Data was taken from [NASA's ExoPlanet Archive](https://exoplanetarchive.ipac.caltech.edu/cgi-bin/TblView/nph-tblView?app=ExoTbls&config=PS). Below is a plot of all planets discovered from 1995-2021 by mass, colored by their Discovery Method.

```{r warning = FALSE, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 5}
pl_exo + theme_bw()
```



### Number of ExoPlanets discovered by facility
This is the number of Exoplanets discovered by facility.You can see that K2 has the most number of Discoveries at `r K2_fac$n` and CoRoT right behind it at `r CoRoT$n`.

```{r warning = FALSE, echo = FALSE, fig.width = 10, fig.height = 5}
fl_exo_plot
```



```{r warning = FALSE, echo = FALSE}

pl_data_clean_2 <- pl_data_clean_1 %>%
  filter(pl_bmassj > 10.00)

count_mass <- count(pl_data_clean_2, pl_bmassj, sort = TRUE)

number <- length(count_mass$pl_bmassj)

```

### Exoplants with mass greater than 10
These are the `r number` Exoplanets with a mass greater than 10.
```{r warning = FALSE, echo = FALSE, fig.align = "center", fig.width = 10, fig.height = 5}

ggplot(pl_data_clean_1, aes(log(pl_bmassj), fill = discoverymethod)) +
  geom_density(alpha = 0.3, bandwidth = 5) +
  theme_bw() +
  ggtitle("ExoPlanets with mass greater than 10") +
  labs(color = "Discovery Method") +
  xlab("Planets Mass (Log)") +
  ylab("Count")
  


```














